%!TEX root = ../main.tex
\section{Problem Definition}
\label{s:problem}
We consider a number of subproblems associated with point-normal triangles.

\begin{enumerate}[label=(\roman*)]
	\item \label{it:problem:fakeNormals}
		% Waarom willen we het weten
		In the introduction we have mentioned that point-normal triangles use a `fake' normal field. Consequently the normal field of a PN triangle does not accurately represent the actual normals. One might wonder why \citeauthor{vlachos2001curved} chose to use a `fake' normal field, instead of the real normals. Since it is possible to compute the `real' normals of the vertices of the tessellated PN-triangle, using the method we present in \crefs{sss:method:normals:realNormals}. 
		%
		%Wat gaan we meten
		In this paper we compare both the computational and the visual performance of the `real' and `fake' normals. 
		% Wat verwachten we
		We do not expect a large difference in visual performance when `real' normals are used. Nor do we suppose that computing the normals based on the geometry will have a significant impact on the computational complexity of point-normal triangles.
		% Inzicht!
		Note that adapting the PN triangle algorithm to use `real' normals does not expand its application domain to include rendering for CAD software. As the smoothness of the rendering, a result of the added geometry, is not present in the actual mesh. 

\iftoggle{PHONG}{
	\item \label{it:problem:CompareWithPhongTesselation}
		\future{2: Compare PN triangles with phong tessellation on the following aspects: performance, continuity, visual. We try to answer the question: When use PN when Phong?}
}	

	\item \label{it:problem:GPUImplementation}
		%Waarom willen we het weten
		One major advantage of point-normal triangles at the time of its introduction (\citeyear{vlachos2001curved}) was that it was fast when computed on the CPU. Since then geometry and tessellation shaders have been introduced into the OpenGL pipeline. Making it possible to compute PN triangles on the GPU. 
		%
		% Wat willen we weten
		We investigate which changes have to be made to the point-normal triangles as proposed by \citeauthor{vlachos2001curved} to fit into a recent OpenGL pipeline (version 4.1).
		%
		% Hoe gaan we het meten
		In this paper we discuss the changes between the CPU implementation proposed by \citeauthor{vlachos2001curved} and our GPU implementation. 
		%
		% Wat verwachten we
		We expect that due to their locality point-normal triangles are extremely suited for computation on the GPU. Allowing us to tessellate triangular meshes faster than is possible on the CPU. 
\end{enumerate}